Covariate analysis of ROSMAP RNASeq data processed using Picard-STAR-HTSeq pipeline from synapse BAM deposited by RUSH

### 2016-11-24 code/Rmd/ROSMAP_RNASeq_Realigned_SynBAM_StarHTSeq.Rmd
Added markdown to compare all versions of ROSMAP

library(ggplot2)
library(reshape2)
library(limma)
library(Biobase)
library(gplots)
library(WGCNA)
library(psych)
library(edgeR)
library(biomaRt)

@@

```{r residual.analysis}
expr = RESIDUAL.GENE_EXPRESSION[!duplicated(RESIDUAL.GENE_EXPRESSION$Gene.ID),-c(1:3)]
rownames(expr) = RESIDUAL.GENE_EXPRESSION$Gene.ID[!(duplicated(RESIDUAL.GENE_EXPRESSION$Gene.ID))]

@@

barplot((PC$sdev^2/sum(PC$sdev^2))[1:10], main = 'Fraction variance explained (top 10 PC)')
p <- GGally::ggpairs(plotdata, mapping = aes(shape=cogdx, color = Batch, size=RINcontinuous),
                     columns = 2:5, diag = list('continuous' = 'densityDiag'),
                     title = 'First 4 PCs of residuals')
p

>>>>

library(ggplot2)
library(reshape2)
library(limma)
library(Biobase)
library(gplots)
library(WGCNA)
library(psych)
library(edgeR)
library(biomaRt)
library(GGally)

@@

```{r residual.analysis, fig.height=5, fig.width=5}
expr = RESIDUAL.GENE_EXPRESSION[!duplicated(RESIDUAL.GENE_EXPRESSION$Gene.ID),-c(1:3)]
rownames(expr) = RESIDUAL.GENE_EXPRESSION$Gene.ID[!(duplicated(RESIDUAL.GENE_EXPRESSION$Gene.ID))]

@@

barplot((PC$sdev^2/sum(PC$sdev^2))[1:10], main = 'Fraction variance explained (top 10 PC)')
```
```{r residual.analysis1, fig.height=15, fig.width=15}
p <- GGally::ggpairs(plotdata, mapping = aes(shape=cogdx, color = Batch, size=RINcontinuous),
                     columns = 2:5, diag = list('continuous' = 'densityDiag'),
                     title = 'First 4 PCs of residuals')
p
